Intersection of non-matching grids of different dimensions

### 2016-09-28 paper_intersections.tex
Introduction nearly done.

%% main text
\section{Introduction}
Structure of introduction:

- motivation for computing mesh intersections, other applications
- basic overview of existing work, approaches
- our contribution
    - new algorithms for element intersectins based on Pl\"ucker coordinates
    - improvement of the front tracking algorithm

\cite{massing_efficient_2013} - Implementation of the Nitche method in Fenics. They need 2d-3d intersections, but only for distribution od quadrature points. 
So they do not store whole intersection data, but only the quad points. The boundary of one domain is partitioned into intersections with elements of the other domain.
Use {\\emph collision relations} ( pairs of faces of boundary and elmements of the background mesh) and {\emph collision maps} 
( map face to all intersections and background element to all intersections, can be constructed from the collision relation), They cite books from computer graphics ..
Mention geometric predicates. Present algorithms for:  find intersection candidates, comput intersections, integrate over complex domains.

The initial problem that occurs when working with incompatible meshes of combined dimensions is the efficient 
computation of intersections of the mesh subdomains, in particular 1D-2D, 1D-3D, 2D-3D.
There is a piece of code in Flow123d at the moment which uses means of analytic geometry. In particular, it computes 
an intersection of a line and a plane in 3D by solving Gaussian elimination. However it is not effiecient
and it does not provide barycentric coordinates explicitly.
In this section, we present our latest work on this problematics.

The topic is studied in the bachelor and master thesis of Viktor Fri{\v s} \cite{fris_dp_2015}, who was supervised by 
Jan B{\v r}ezina.
They suggested a solution, based on \cite{yuan_efficient_2003} for the two aspects of the problem: 
\begin{enumerate}[itemsep=-3pt]
\item an efficient identification of the intersecting pairs of elements,
\item an efficient computation of the actual intersection for the single element pair.
\end{enumerate}
The algorithm is based on the methods used in the computer graphics, in particular for the task (b) \plucker
coordinates are employed to efficiently compute 1D-2D intersection in three-dimensional space.

@@

@@

>>>>

%% main text
\section{Introduction}
Structure:
\begin{itemize}
 \item Introduction of the problem. 
 \item Overview of methods using some sort of mesh intersections.
 \item Our motivation from groundwater applications.
 \item Existing algorithms.
 \item Our contribution:
    new algorithms for element intersections based on \plucker coordinates,
    improvement of the front tracking algorithm
 \item Paper overview   
\end{itemize}

The grid intersection algorithms are crucial for several techniques that tries to overcome some limitations of the classical finite element method.
The Chimera method \cite{brezzi_analysis_2001} also called overset grid and similar Nitche method \cite{massing_efficient_2013}
allow solution of the problems with changing geometry as in the fluid-structure problems. 
The Mortar method \cite{belgacem_mortar_1999} allows domain decomposition, independent meshing of domains, and supports sliding boundaries.
However our primal motivation is usage of XFEM methods and non-matching meshes of mixed dimension in groundwater models.

The realistic models of groundwater processes including the transport processes and geomechanics have to deal with 
a complex nature of geological formations including the fractures and wells. Although of small scale, these features may have significant impact 
on the global behavior of the system and their representation in the numerical model is imperative.
One possible approach is to model fractures and wells as lower dimensional objects and introduce their coupling with the surrounding continuum. 
The discretization then leads to the meshes of mixed dimensions, i.e. composed of elements of different dimension. This approach 
called mixed-dimensional analysis in the mechanics \cite{bournival_mesh-geometry_2008} is also studied in the groundwater context, see e.g. 
\cite{martin_modeling_2005}, \cite{fumagalli_numerical_2011}, \cite{brezina_analysis_2015} and 
already adopted by some groundwater simulation software, e.g FeFlow \cite{trefry_feflow:_2007} and Flow123d \cite{flow123d}.
Nevertheless as the complexity of the geometry increase (e.g. when lot of fractures are randomly generated) the compatible meshing becomes painful or even 
impossible. In order to avoid these difficulties we may discretize the continuum and every fracture and well independently getting a non-matching 
(or incompatible) mesh of mixed dimensions and then apply XFEM to represent jumps of the solution on the fractures or singularities 
around the wells. The prerequisity for such approach is a fast and robust algorithm for calculating intersections of individual meshes.

We consider a composed mesh $\mathcal T$ consisting of meshes $\mathcal T_i$ of dimensions $d_i \in \{1,2,3\}$, $i=1,\dots,N_\mathcal{T}$. 
We assume that the meshes $\mathcal T_i$ are connected, that is the graph having elements for vertices and their nighbouring for edges is connected.
We also assume that no submesh intersect itself. Further we assume that only $\mathcal{T}_1$ have $d_1=3$ and $d_i < 3$ for $i>1$. 
The mesh intersection problem is to find all pairs of elements $L\in \mathcal{T}_i$, $K\in \mathcal{T}_j$, $i\ne j$ that have non-empty intersection 
and compute that intersection. Every (possibly degenerated) intersection polygon (IP) is determined by its corners called intersection corners (IC).
For every IC we want to compute its barycentric coordinates on $K$ and on $L$.

The mesh intersection problem consists of the two parts: First, generate a set of candidate pairs $(K, L)$. Second, compute the intersection for particular pair.
In order to get candidate pairs efficiently, the existing algorithms use either various space trees \cite{massing_efficient_2013} or front tracing
\cite{gander_algorithm_2013} or both \cite{elsheikh_reliable_2012} as in our approach. To compute the actual intersections, we 
use the \plucker coordinates for the line-triangle intersections and a modification of the  Platis and Theoharis algorithm \cite{platis_fast_2003}
for the line-tetrahedron intersections. These are used as the building block for the triangle-triangle and the trinagle-tetrahedron cases.

They suggested a solution, based on \cite{yuan_efficient_2003} for the two aspects of the problem: 
\begin{enumerate}[itemsep=-3pt]
\item an efficient identification of the intersecting pairs of elements,
\item an efficient computation of the actual intersection for the single element pair.
\end{enumerate}
The algorithm is based on the methods used in the computer graphics, in particular for the task (b) \plucker
coordinates are employed to efficiently compute 1D-2D intersection in three-dimensional space.

@@

adaptive precision arithmetic 
    \cite{elsheikh_reliable_2012} (based on edge-triangle intersections, 
        use calculations that are similar to usage of \plucker coordinates), 
    \cite{shewchuk_adaptive_1997}

@@

USED:
\cite{massing_efficient_2013} - Implementation of the Nitche method in Fenics. They need 2d-3d intersections, but only for distribution od quadrature points. 
So they do not store whole intersection data, but only the quad points. The boundary of one domain is partitioned into intersections with elements of the other domain.
Use {\\emph collision relations} ( pairs of faces of boundary and elmements of the background mesh) and {\emph collision maps} 
( map face to all intersections and background element to all intersections, can be constructed from the collision relation), They cite books from computer graphics ..
Mention geometric predicates. Present algorithms for:  find intersection candidates, comput intersections, integrate over complex domains.
